Dark matter halo shape at $z=0$ in the Auriga simulations: radial evolution and alignments with the stellar disk

### 2019-07-18 Document/paper.tex
abstract

% Abstract of the paper
\begin{abstract}
We present shape measurements of dark matter halos in a suit
of 30 cosmological simulations from the Auriga project.
For all measurements we compare the results in full
magnetohydrodynamics against dark matter only physics.
We find a strong influence of baryons in making dark matter halos rounder at all
radii compared to its dark matter only counterparts.
This change in triaxility its more pronounced towards the inner
regions of the halo.
At distances close to the disk rounder dark matter distributions
correlate with massive stellar disks and low gas density.
The dark matter shape shows a strong alignment with the
stellar disk shape as a function of radius, the stronger aligmnet is
found at $~50$kpc, this alignment weakens at smaller and larger radii. 
In dark matter only simulations the time evolution of the shape
measured at the virial radius correlates with the radial shape
evolution at present day.  
However, this correlation is lost once the baryonic effects are
included. 
We conclude that in our simulation suite that baryonic physics
produces rounder halos with a strong correlation between its inner
shape and the stellar and gaseous properties of the disk.
\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}
We present shape measurements of dark matter halos at redshift $z=0$
in a suite of 30 cosmological simulations from the Auriga project.
For all measurements we compare the results in full
magnetohydrodynamics against dark matter only physics.
We find a strong influence of baryons in making dark matter halos
rounder at all radii compared to its dark matter only counterparts.
This change in triaxility its more pronounced towards the inner
regions of the halo.
In simulations with baryons we measure a twist in the dark matter
shape as a function of radial distance.
We present this effect as a changing degree of halo shape alignment
with the stellar disk shape as a function of radius; the stronger
alignment is found at $0.25R_{200}\sim56$ kpc. 
This twisting in halo shape is almost absent from dark matter only
simulations. 
We show that a coherent halo shape with radius correlates with low
triaxility values.  
At distances close to the disk, rounder and coherent dark matter
distributions correlate with massive stellar disks and low gas density. 
In a comparison against observational constraints of dark matter halo
triaxiality for the Milky Way we find that $20\%$ of the galaxies in
our sample are consitent with observational results that favor
$b/a\approx 1$ and $c/a>0.77$ but are at odds with other results that
favor $c/a\approx0.44$. 
\end{abstract}
